Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-13 R0V0.tex
Changes on the definition of the set Xi and and the Proof of Proposition 1

Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.

@@

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}(\mathscr{C}_k)\times n}$ as
	\begin{equation*}
		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\mathbin{\mathtt{card}}(\mathscr{C}_k)]}\;,
	\end{equation*}	
	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.

   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$. The existence of $p$ cliques implies that there exist matrices $F_1,\ldots,F_p$ such that the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k
  	\end{equation*}
  	holds.

>>>>

Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij})\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.

@@

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathbin{\mathtt{card}}(\mathscr{C}_k))$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ as
	\begin{equation*}
		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\dim_k]}\;,
	\end{equation*}	
	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.

   Denote the left-hand side of the MI~\eqref{eq:MI formulation} by $T$. The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\dim_k}\to\mathbb{R}^{\dim_k\times \dim_k}$, where $k\in\mathbb{N}_{[1,p]}$, such that the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k
  	\end{equation*}
  	holds.
